Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
paper: add final graphs for Mantle
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Mantle}\label{mantle}

\subsubsection{Experiment: FileBench}\label{experiment-filebench}

\subsubsection{Experiment: OpenSSL
Compile}\label{experiment-openssl-compile}

@@

>>>>

@@

\subsection{Mantle}

\subsection{MDS as a Sequencer}
\begin{figure}[h]
\centering
\includegraphics{figures/mantle-seq-thruput.png}
\caption{A ZLog sequencer that uses the CephFS metadata cluster enjoys all the benefits of the MDS recovery ("Sequencer Recovery") and load balancing protocols (``Mantle Load Balancing''). The ``2 Seq'' curves are the throughputs of 1 sequencer when an additional sequencer is running in the background generating load. The ``Sequencer Baseline'' has no background sequencers.}
\label{fig:mantle-seq-thruput.png}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics{figures/mantle-cpu-utilization-annotate.png}
\caption{The sequencer using Mantle in Figure~\ref{fig:mantle-seq-thruput.png} migrates to a new MDS immediately because its uses a policy designed for bursty workloads. This is a trace of the same workload running twice: once with a single MDS and once with Mantle.}
\label{fig:mantle-cpu-utilization}
\end{figure}

\subsection{Load Balancing}

\subsection{Recovery}
